\subsubsection{Data Dictionary}

This data dictionary documents the structure of the ModLearn relational database on a table-by-table basis.

\begingroup
\small
\renewcommand{\arraystretch}{1.15}

\newcommand{\ddheader}{
\toprule
\textbf{Attribute Name} & \textbf{Description} & \textbf{Data Type} & \textbf{Constraints} & \textbf{References} \\
\midrule
\endfirsthead
\toprule
\textbf{Attribute Name} & \textbf{Description} & \textbf{Data Type} & \textbf{Constraints} & \textbf{References} \\
\midrule
\endhead
\bottomrule
\endfoot
}

\paragraph{Table: User}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of each user. & Text & Primary key, not null & -- \\
name & Full name of the user. & Text & Not null & -- \\
email & Email address used by the user account. & Text & Not null, unique & -- \\
emailVerified & Indicates whether the email address has been verified. & Boolean & Not null, default false & -- \\
image & Profile image URL or path. & Text & Nullable & -- \\
createdAt & Date and time when the user record was created. & Timestamp & Not null, default now & -- \\
updatedAt & Date and time when the user record was last updated. & Timestamp & Not null, auto update & -- \\
username & System username of the user. & Text & Unique, nullable & -- \\
displayUsername & Display name shown publicly in the platform. & Text & Nullable & -- \\
role & Role of the user, such as learner or administrator. & Text & Nullable & -- \\
banned & Indicates whether the user account is banned. & Boolean & Default false & -- \\
banReason & Reason for account ban. & Text & Nullable & -- \\
banExpires & Date and time when the ban expires. & Timestamp & Nullable & -- \\
\end{longtable}

\paragraph{Table: Session}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the session. & Text & Primary key, not null & -- \\
expiresAt & Session expiration date and time. & Timestamp & Not null & -- \\
token & Unique token used for session authentication. & Text & Not null, unique & -- \\
createdAt & Date and time when the session was created. & Timestamp & Not null, default now & -- \\
updatedAt & Date and time when the session was last updated. & Timestamp & Not null, auto update & -- \\
ipAddress & IP address of the client creating the session. & Text & Nullable & -- \\
userAgent & Browser or device agent string. & Text & Nullable & -- \\
userId & User who owns the session. & Text & Not null, foreign key & User.id \\
impersonatedBy & User or actor that impersonated the session owner, if applicable. & Text & Nullable & -- \\
\end{longtable}

\paragraph{Table: Account}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the linked account. & Text & Primary key, not null & -- \\
accountId & Identifier assigned by the authentication provider. & Text & Not null & -- \\
providerId & Authentication provider name or identifier. & Text & Not null & -- \\
userId & User who owns the linked account. & Text & Not null, foreign key & User.id \\
accessToken & Access token issued by the provider. & Text & Nullable & -- \\
refreshToken & Refresh token issued by the provider. & Text & Nullable & -- \\
idToken & Identity token issued by the provider. & Text & Nullable & -- \\
accessTokenExpiresAt & Expiration date and time of the access token. & Timestamp & Nullable & -- \\
refreshTokenExpiresAt & Expiration date and time of the refresh token. & Timestamp & Nullable & -- \\
scope & Access scope granted by the provider. & Text & Nullable & -- \\
password & Stored password or credential field when applicable. & Text & Nullable & -- \\
createdAt & Date and time when the linked account was created. & Timestamp & Not null, default now & -- \\
updatedAt & Date and time when the linked account was last updated. & Timestamp & Not null, auto update & -- \\
\end{longtable}

\paragraph{Table: Verification}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the verification record. & Text & Primary key, not null & -- \\
identifier & Identifier used in the verification flow. & Text & Not null & -- \\
value & Verification value or token. & Text & Not null & -- \\
expiresAt & Expiration date and time of the verification record. & Timestamp & Not null & -- \\
createdAt & Date and time when the verification record was created. & Timestamp & Not null, default now & -- \\
updatedAt & Date and time when the verification record was last updated. & Timestamp & Not null, default now, auto update & -- \\
\end{longtable}

\paragraph{Table: Category}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the category. & UUID & Primary key, not null & -- \\
title & Category name used for course classification. & Text & Not null & -- \\
description & Description of the category. & Text & Nullable & -- \\
slug & URL-friendly identifier of the category. & Text & Unique, nullable & -- \\
\end{longtable}

\paragraph{Table: Course}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the course. & UUID & Primary key, not null & -- \\
creatorId & User who created or manages the course. & Text & Not null, foreign key & User.id \\
title & Course title. & Text & Not null & -- \\
description & General description of the course. & Text & Nullable & -- \\
thumbnailImageId & File used as the course thumbnail image. & UUID & Nullable, foreign key & File.id \\
isPublished & Indicates whether the course is published. & Boolean & Not null, default false & -- \\
publishedAt & Date and time when the course was published. & Timestamp & Nullable & -- \\
isAvailable & Indicates whether the course is currently available to users. & Boolean & Not null, default true & -- \\
isDeleted & Indicates whether the course is soft deleted. & Boolean & Not null, default false & -- \\
deletedAt & Date and time when the course was marked deleted. & Timestamp & Nullable & -- \\
createdAt & Date and time when the course record was created. & Timestamp & Not null, default now & -- \\
updatedAt & Date and time when the course record was last updated. & Timestamp & Not null, default now, auto update & -- \\
\end{longtable}

\paragraph{Table: CourseLesson}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the lesson. & UUID & Primary key, not null & -- \\
courseId & Course to which the lesson belongs. & UUID & Not null, foreign key & Course.id \\
lessonOrder & Ordering number of the lesson within the course. & Integer & Not null, unique within course & -- \\
title & Lesson title. & Text & Not null & -- \\
description & Lesson description or summary. & Text & Nullable & -- \\
thumbnailImageId & File used as the lesson thumbnail image. & UUID & Nullable, foreign key & File.id \\
duration & Lesson duration. & BigInt & Nullable & -- \\
releaseDate & Planned or actual release date of the lesson. & Date & Nullable & -- \\
fileId & Media file used by the lesson. & UUID & Nullable, foreign key & File.id \\
addedAt & Date and time when the lesson was added to the course. & Timestamp & Not null, default now & -- \\
createdAt & Date and time when the lesson record was created. & Timestamp & Not null, default now & -- \\
updatedAt & Date and time when the lesson record was last updated. & Timestamp & Not null, default now, auto update & -- \\
\end{longtable}

\paragraph{Table: CourseCategory}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the course-category link. & UUID & Primary key, not null & -- \\
courseId & Course in the relationship. & UUID & Not null, foreign key, unique pair & Course.id \\
categoryId & Category in the relationship. & UUID & Not null, foreign key, unique pair & Category.id \\
\end{longtable}

\paragraph{Table: CoursePricing}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the pricing record. & UUID & Primary key, not null & -- \\
courseId & Course to which the price applies. & UUID & Not null, foreign key & Course.id \\
price & Price amount for the course. & Decimal(10,2) & Not null & -- \\
currency & Currency code of the price. & Text & Not null & -- \\
effectiveFrom & Start date and time when the price becomes active. & Timestamp & Not null & -- \\
effectiveTo & End date and time when the price stops being active. & Timestamp & Nullable & -- \\
createdBy & User who created the pricing record. & Text & Not null, foreign key & User.id \\
createdAt & Date and time when the pricing record was created. & Timestamp & Not null, default now & -- \\
\end{longtable}

\paragraph{Table: File}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the file metadata record. & UUID & Primary key, not null & -- \\
uploaderId & User who uploaded the file. & Text & Not null, foreign key & User.id \\
uploadedAt & Date and time when the file was uploaded. & Timestamp & Not null, default now & -- \\
name & Original file name. & Text & Not null & -- \\
size & File size. & BigInt & Not null & -- \\
mimeType & MIME type of the file. & Text & Not null & -- \\
extension & File extension. & Text & Not null & -- \\
checksum & Checksum used for file integrity. & Text & Not null & -- \\
isDeleted & Indicates whether the file is soft deleted. & Boolean & Not null, default false & -- \\
deletedAt & Date and time when the file was marked deleted. & Timestamp & Nullable & -- \\
\end{longtable}

\paragraph{Table: Storage}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the storage record. & UUID & Primary key, not null & -- \\
fileId & File metadata record linked to the stored object. & UUID & Not null, foreign key & File.id \\
storageProvider & Name of the storage provider. & Text & Not null & -- \\
bucket & Storage bucket or container name. & Text & Nullable & -- \\
storageKey & Object key or path in the storage system. & Text & Not null & -- \\
cdnUrl & Public or CDN access URL for the file. & Text & Nullable & -- \\
\end{longtable}

\paragraph{Table: Order}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the order. & UUID & Primary key, not null & -- \\
userId & User who placed the order. & Text & Not null, foreign key & User.id \\
totalAmount & Total amount charged in the order. & Decimal(10,2) & Not null & -- \\
currency & Currency code of the order. & Text & Not null & -- \\
itemType & Type of item being purchased. & Enum & Not null, values defined by cart item enum & -- \\
courseId & Course associated with the order, when applicable. & UUID & Nullable, foreign key & Course.id \\
status & Current order status. & Enum & Not null, values: PENDING, PAID, FAILED, REFUNDED & -- \\
createdAt & Date and time when the order was created. & Timestamp & Not null, default now & -- \\
updatedAt & Date and time when the order was last updated. & Timestamp & Not null, default now, auto update & -- \\
\end{longtable}

\paragraph{Table: Payment}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the payment record. & UUID & Primary key, not null & -- \\
orderId & Order paid by this payment record. & UUID & Not null, foreign key & Order.id \\
providerTransactionId & Transaction identifier from the payment provider. & Text & Not null & -- \\
provider & Name of the payment provider. & Text & Not null & -- \\
amount & Amount processed in the payment. & Decimal(10,2) & Not null & -- \\
currency & Currency code of the payment. & Text & Not null & -- \\
status & Current payment status. & Enum & Not null, values: INITIATED, SUCCESS, FAILED & -- \\
paidAt & Date and time when the payment was completed. & Timestamp & Nullable & -- \\
failureReason & Explanation of payment failure, if any. & Text & Nullable & -- \\
\end{longtable}

\paragraph{Table: CoursePurchase}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the purchase record. & UUID & Primary key, not null & -- \\
courseId & Purchased course. & UUID & Not null, foreign key & Course.id \\
userId & User who purchased the course. & Text & Not null, foreign key, unique pair & User.id \\
purchasedAt & Date and time when the course was purchased. & Timestamp & Not null, default now & -- \\
price & Purchase price recorded at transaction time. & Decimal(10,2) & Not null & -- \\
status & Current purchase status. & Text & Not null & -- \\
orderId & Source order related to the purchase. & UUID & Nullable, foreign key & Order.id \\
\end{longtable}

\paragraph{Table: UserLibrary}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the library entry. & UUID & Primary key, not null & -- \\
userId & User who owns the library entry. & Text & Not null, foreign key, unique pair & User.id \\
courseId & Course granted to the user library. & UUID & Not null, foreign key, unique pair & Course.id \\
orderId & Order from which the library access originated. & UUID & Not null, foreign key & Order.id \\
acquiredAt & Date and time when access was granted. & Timestamp & Not null, default now & -- \\
expiresAt & Date and time when access expires, if limited. & Timestamp & Nullable & -- \\
\end{longtable}

\paragraph{Table: WatchProgress}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the watch-progress record. & UUID & Primary key, not null & -- \\
courseId & Course associated with the progress record. & UUID & Not null, foreign key & Course.id \\
courseLessonId & Lesson associated with the progress record. & UUID & Not null, foreign key, unique pair with userId & CourseLesson.id \\
userId & User whose progress is being tracked. & Text & Not null, foreign key, unique pair with courseLessonId & User.id \\
lastPosition & Last playback position reached by the learner. & BigInt & Not null & -- \\
duration & Full lesson duration used for progress calculation. & BigInt & Not null & -- \\
isCompleted & Indicates whether the lesson was completed. & Boolean & Not null, default false & -- \\
updatedAt & Date and time when the progress record was last updated. & Timestamp & Not null, default now, auto update & -- \\
deviceType & Device category used during viewing. & Text & Nullable & -- \\
\end{longtable}

\paragraph{Table: CourseLessonView}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the lesson-view record. & UUID & Primary key, not null & -- \\
courseLessonId & Lesson viewed in the event record. & UUID & Not null, foreign key & CourseLesson.id \\
userId & User who viewed the lesson, when authenticated. & Text & Nullable, foreign key & User.id \\
sessionId & Session associated with the view event. & Text & Nullable, foreign key & Session.id \\
viewedAt & Date and time when the lesson was viewed. & Timestamp & Not null, default now & -- \\
watchDuration & Duration watched during the view event. & BigInt & Default 0 & -- \\
deviceType & Device category used for the lesson view. & Text & Nullable & -- \\
\end{longtable}

\paragraph{Table: CourseReview}
\begin{longtable}{L{2.6cm}L{4.5cm}L{2.1cm}L{3.3cm}L{2.2cm}}
\ddheader
id & Unique identifier of the review. & UUID & Primary key, not null & -- \\
courseId & Course being reviewed. & UUID & Not null, foreign key, unique pair with userId & Course.id \\
userId & User who submitted the review. & Text & Not null, foreign key, unique pair with courseId & User.id \\
rating & Numeric rating submitted by the user. & Integer & Not null, check 1 to 5 & -- \\
comment & Written review comment. & Text & Nullable & -- \\
isVisible & Indicates whether the review is visible publicly. & Boolean & Not null, default true & -- \\
hiddenAt & Date and time when the review was hidden. & Timestamp & Nullable & -- \\
hiddenBy & User who moderated or hid the review. & Text & Nullable, foreign key & User.id \\
moderationReason & Reason for hiding or moderating the review. & Text & Nullable & -- \\
createdAt & Date and time when the review was created. & Timestamp & Not null, default now & -- \\
updatedAt & Date and time when the review was last updated. & Timestamp & Not null, default now, auto update & -- \\
\end{longtable}

\subsubsection{Data Type and Constraint Summary}

\paragraph{Data Type Summary}
\begin{longtable}{L{2.5cm}L{7.1cm}L{4.1cm}}
\toprule
\textbf{Data Type} & \textbf{Usage} & \textbf{Example Attributes} \\
\midrule
\endfirsthead
\toprule
\textbf{Data Type} & \textbf{Usage} & \textbf{Example Attributes} \\
\midrule
\endhead
\bottomrule
\endfoot
Text & Used for general string data such as names, titles, comments, emails, tokens, role labels, and provider identifiers. & name, email, title, comment, token, role \\
UUID & Used for unique identifiers in content, media, commerce, and analytics tables. & course.id, file.id, order.id \\
Integer & Used for whole-number values that do not require very large storage. & lessonOrder, rating \\
BigInt & Used for large numeric values such as file size, duration, watch duration, and playback position. & size, duration, lastPosition, watchDuration \\
Decimal(10,2) & Used for monetary values where decimal precision must be preserved. & price, totalAmount, amount \\
Boolean & Used for true-or-false status fields. & isPublished, isDeleted, isCompleted, isVisible, emailVerified \\
Timestamp & Used for date and time values related to creation, updates, uploads, purchases, views, and expiration. & createdAt, updatedAt, uploadedAt, viewedAt, expiresAt \\
Date & Used when only the calendar date is needed without time details. & releaseDate \\
Enum & Used for controlled values in workflow-related fields. & order status, payment status, cart item type \\
\end{longtable}

\paragraph{Constraint Summary}
\begin{longtable}{L{3cm}L{6.8cm}L{3.9cm}}
\toprule
\textbf{Constraint} & \textbf{Purpose} & \textbf{Example} \\
\midrule
\endfirsthead
\toprule
\textbf{Constraint} & \textbf{Purpose} & \textbf{Example} \\
\midrule
\endhead
\bottomrule
\endfoot
Primary key & Ensures that each row in a table has a unique identity. & user.id, course.id \\
Foreign key & Connects one table to another and preserves relational consistency. & session.userId references user.id \\
Not null & Ensures that a required field cannot be left empty. & course.title, order.userId \\
Unique & Prevents duplicate values in fields that must remain distinct. & user.email, session.token \\
Composite unique & Prevents duplicate relationship records across more than one column. & one review per user per course \\
Default value & Automatically assigns an initial value when none is provided. & isPublished default false, createdAt default now \\
Check constraint & Restricts values to a valid range or rule. & rating must be between 1 and 5 \\
\end{longtable}

\endgroup
