\documentclass{article}

\usepackage{geometry}
\geometry{margin=1in}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\title{modlearn}
\author{}
\date{}

\begin{document}

\maketitle
\onehalfspacing

\section{Introduction}

\subsection{Background and Significance}

The project requirement is to create a streaming platform for learning. This idea comes from the growing importance of digital education and the increasing use of online video platforms in everyday life. Many learners now prefer studying through video content because it is easier to access, easier to understand, and more flexible than traditional classroom-only learning. As a result, educational platforms that use streaming technology have become an important part of modern learning environments.

The significance of this project is that it applies the streaming platform model to educational purposes. Instead of using streaming only for entertainment, this project uses it to support knowledge delivery, self-paced study, and easier access to learning materials. A learning streaming platform can help users study anytime and anywhere, repeat lessons when necessary, and follow content in a more organized way. This is especially useful for students, independent learners, and anyone who wants convenient access to educational content.

In addition, this project is important from a system development perspective. It requires the design of a platform that can manage content, support user access, and provide a smooth viewing experience across devices. Therefore, modlearn is both an educational solution and a practical software engineering project that explores how streaming technology can be adapted for learning.

\subsection{Objectives}

The main objective of this project is to develop \textbf{modlearn} as a learning streaming platform that allows users to access educational video content through a modern and organized system.

The specific objectives of the project are as follows:
\begin{enumerate}
    \item To design and develop a platform for streaming educational content.
    \item To provide users with an easy way to browse, select, and watch learning materials online.
    \item To create a responsive and organized system that supports effective learning and future platform growth.
\end{enumerate}

\section{Requirement}

\subsection{Requirement Summary}

ModLearn is a web-based digital learning platform intended to support the discovery, acquisition, access, and continued consumption of structured online course content. The platform is expected to serve both public users and authenticated learners while also providing controlled administrative capabilities for maintaining the course catalog, lessons, classifications, pricing, reviews, and reporting data.

From the learner perspective, the system is expected to provide a complete learning-access flow. Users should be able to discover available courses, review course information, obtain access through valid ownership, continue lessons from previous progress, and receive discovery support through recommendation and continue-watching features. The system is therefore not limited to one-time page access; it must support continuity across repeated visits and sessions.

From the operational perspective, the platform must enable authorized administrators to manage the structure and release state of learning content. This includes maintaining courses, lessons, categories, associated media assets, monetization settings, moderation actions, and analytics views. Administrative behavior must remain separated from public or learner behavior through role-based access control and controlled access boundaries.

\subsection{Stakeholders and Scope}

\begin{tabularx}{\textwidth}{L{3cm}Y}
\toprule
\textbf{Stakeholder} & \textbf{Primary concern} \\
\midrule
Public visitor & Discover visible courses and inspect public course information \\
Learner & Access owned content, resume progress, and interact with course feedback features \\
Administrator & Maintain content, pricing, classifications, media, moderation, and analytics \\
System owner & Ensure the platform supports controlled delivery, monetization, and operational oversight \\
\bottomrule
\end{tabularx}

\end{document}
