\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[dvipsnames]{xcolor}
\usepackage{array}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{tabularx}
\usepackage[most]{tcolorbox}

\hypersetup{
	colorlinks=true,
	linkcolor=MidnightBlue,
	urlcolor=MidnightBlue
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.5em}
\pagestyle{plain}

\newcolumntype{Y}{>{\raggedright\arraybackslash}X}
\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}

\newtcolorbox{notebox}{
	colback=gray!6,
	colframe=gray!35,
	boxrule=0.5pt,
	arc=2mm,
	left=4mm,
	right=4mm,
	top=2mm,
	bottom=2mm
}

\title{\textbf{ModLearn Requirements Overview}}
\author{}
\date{}

\begin{document}
\maketitle

\section*{1. Requirement Summary}
ModLearn is a web-based digital learning platform intended to support the discovery, acquisition, access, and continued consumption of structured online course content. The platform is expected to serve both public users and authenticated learners while also providing controlled administrative capabilities for maintaining the course catalog, lessons, classifications, pricing, reviews, and reporting data.

From the learner perspective, the system is expected to provide a complete learning-access flow. Users should be able to discover available courses, review course information, obtain access through valid ownership, continue lessons from previous progress, and receive discovery support through recommendation and continue-watching features. The system is therefore not limited to one-time page access; it must support continuity across repeated visits and sessions.

From the operational perspective, the platform must enable authorized administrators to manage the structure and release state of learning content. This includes maintaining courses, lessons, categories, associated media assets, monetization settings, moderation actions, and analytics views. Administrative behavior must remain separated from public or learner behavior through role-based access control and controlled access boundaries.

\section*{2. Document Boundary}
\begin{notebox}
This document is \textbf{not} the detailed functional requirement specification.

It captures the \textbf{higher-level system requirements} that define what ModLearn must provide as a product. Detailed functional requirements, non-functional requirements, interface requirements, and data requirements should be derived from this document in separate sections or separate documents.
\end{notebox}

\section*{3. Stakeholders and Scope}
\begin{tabularx}{\textwidth}{L{3cm}Y}
\toprule
\textbf{Stakeholder} & \textbf{Primary concern} \\
\midrule
Public visitor & Discover visible courses and inspect public course information \\
Learner & Access owned content, resume progress, and interact with course feedback features \\
Administrator & Maintain content, pricing, classifications, media, moderation, and analytics \\
System owner & Ensure the platform supports controlled delivery, monetization, and operational oversight \\
\bottomrule
\end{tabularx}

\section*{4. System-Level Requirements}
\renewcommand{\arraystretch}{1.2}
\begin{longtable}{L{1.8cm}L{9.4cm}L{2.1cm}}
\toprule
\textbf{ID} & \textbf{Requirement Statement} & \textbf{Verify} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Requirement Statement} & \textbf{Verify} \\
\midrule
\endhead
\bottomrule
\endfoot

REQ-01 & The system shall provide a web-based platform for browsing, accessing, and managing digital learning content. & Test \\
REQ-02 & The system shall distinguish between public access, authenticated learner access, and administrative access, and shall restrict system capabilities according to the applicable access level. & Test \\
REQ-03 & The system shall expose to public users only course content that has been intentionally released for public visibility and access. & Test \\
REQ-04 & The system shall allow users to discover available courses through catalog browsing, course detail views, and classification or search-based navigation supported by the platform. & Test \\
REQ-05 & The system shall allow authorized administrators to create, update, classify, publish, unpublish, and maintain courses and lessons. & Test \\
REQ-06 & The system shall allow authorized administrators to manage supporting catalog structures, including categories, lesson ordering, and related media assets. & Test \\
REQ-07 & The system shall support controlled acquisition of course access and shall grant protected learning access only after valid user entitlement has been established. & Test \\
REQ-08 & The system shall provide authenticated learners with access to their owned learning content through a personal library or equivalent owned-content view. & Test \\
REQ-09 & The system shall preserve learner continuity by storing and retrieving lesson progress, completion state, resume targets, and continue-watching information. & Test \\
REQ-10 & The system shall allow eligible learners to submit ratings and reviews for content they are authorized to evaluate. & Test \\
REQ-11 & The system shall allow authorized administrators to moderate the visibility or removal of learner reviews according to platform rules. & Test \\
REQ-12 & The system shall provide learner discovery support through recommendation and popularity-based or recency-based content views derived from available platform data. & Analysis and test \\
REQ-13 & The system shall provide administrators with reporting views sufficient to monitor course performance, lesson engagement, and viewing activity. & Test \\
REQ-14 & The system shall support administrative control over course pricing and related monetization settings that govern learner purchase eligibility. & Test \\
REQ-15 & The system shall protect learner-specific and administrator-specific operations from unauthorized access. & Test and inspection \\

\end{longtable}

\section*{5. Decomposition Guidance}
The requirements in this document should be decomposed into more detailed requirement classes:
\begin{itemize}[leftmargin=1.5em]
	\item \textbf{Functional requirements}: detailed system behaviors such as sign-in, course management, watch progress, reviews, pricing, and analytics flows.
	\item \textbf{Non-functional requirements}: quality constraints such as security, performance, usability, availability, and maintainability.
	\item \textbf{Interface and data requirements}: external interfaces, role boundaries, and core data objects such as users, courses, lessons, categories, reviews, purchases, and progress records.
\end{itemize}

\section*{6. Basis for This Structure}
This structure follows current requirements-engineering guidance that separates stakeholder expectations and higher-level system requirements from lower-level technical or functional requirements.

\begin{enumerate}[leftmargin=1.5em]
	\item NASA, \emph{Stakeholder Expectations Definition}: \href{https://www.nasa.gov/reference/4-1-stakeholder-expectations-definition/}{nasa.gov}
	\item NASA, \emph{Technical Requirements Definition}: \href{https://www.nasa.gov/reference/4-2-technical-requirements-definition/}{nasa.gov}
	\item INCOSE Requirement Working Group, \emph{Guide to Writing Requirements v4 Overview}: \href{https://www.incose.org/docs/default-source/working-groups/requirements-wg/shared_gtwr/gtwrv4overview120923a.pdf}{incose.org}
	\item ISO/IEC/IEEE 29148 overview: \href{https://www.iso.org/standard/72089.html}{iso.org}
\end{enumerate}

\end{document}
